\newpage
\addcontentsline{toc}{section}{\numberline{}REFERENCES}
%\newgeometry{left=3.5cm,top=0cm,right=2cm,bottom=2cm}
\begin{thebibliography}{9}

        \bibitem{smith2013}
                Smith, Steven W.
                \emph{The scientists and engineers guide to digital signal processing.}
                California Technical Publishing, 2013. Print.

        \bibitem{kassler1966}
                Kassler, Michael. 
                \emph{Toward musical information retrieval.} 
                Perspectives of New Music (1966): 59-67.

        \bibitem{andel1975}
                Andel, James. 
                \emph{On the segmentation and analysis of continuous musical sound by digital computer.} 
                Diss. Stanford University, 1975.

        \bibitem{Tzanetakis2002a}
                Tzanetakis, George, and Perry Cook. 
                \emph{Manipulation, analysis and retrieval systems for audio signals.} 
                Princeton, NJ, USA: Princeton University, 2002.

        \bibitem{alghoniemy1999}
                Alghoniemy, Masoud, and Ahmed H. Tewfik. 
                \emph{Rhythm and periodicity detection in polyphonic music.} 
                Multimedia Signal Processing, 1999 IEEE 3rd Workshop on. Ieee, 1999.

         \bibitem{byrd2002}
                Byrd, Donald, and Tim Crawford. 
                \emph{Problems of music information retrieval in the real world.} 
                Information processing and management 38.2 (2002): 249-272.

         \bibitem{saunders1996}
                Saunders, John. 
                \emph{Real-time discrimination of broadcast speech/music.} 
                icassp. Vol. 96. 1996.

         \bibitem{wold1996}
                Wold, Erling, et al. 
                \emph{Content-based classification, search, and retrieval of audio.} 
                IEEE multimedia 3.3 (1996): 27-36.

         \bibitem{scheirer1997}
                Scheirer, Eric, and Malcolm Slaney. 
                \emph{Construction and evaluation of a robust multifeature speech/music discriminator.} 
                Acoustics, Speech, and Signal Processing, 1997. ICASSP-97., 1997 IEEE International Conference on. Vol. 2. IEEE, 1997.

         \bibitem{Casey2008}
                Casey, Michael A., et al. 
                \emph{Content-based music information retrieval: Current directions and future challenges.} 
                Proceedings of the IEEE 96.4 (2008): 668-696.

         \bibitem{Kaminskas2012}
                Kaminskas, Marius, and Francesco Ricci.
                \emph{Contextual music information retrieval and recommendation: State of the art and challenges.} 
                Computer Science Review 6.2 (2012): 89-119.

        \bibitem{Tzanetakis2002}
                Tzanetakis, George, and Perry Cook, Musical genre classification based on audio signals
                \emph{IEEE Transactions on Speech and Audio Processing},
                10.5 (2002)

        \bibitem{Scaringella2006}
                Scaringella, Nicolas, Giorgio Zoia, and Daniel Mlynek. 
                \emph{Automatic genre classification of music content: a survey.} 
                IEEE Signal Processing Magazine 23.2 (2006): 133-141.

        \bibitem{Perrot1999}
                Perrot, David, and Robert Gjerdigen. 
                \emph{Scanning the dial: An exploration of factors in the identification of musical style.} 
                Proceedings of the 1999 Society for Music Perception and Cognition. 1999.

        \bibitem{Lippens2004}
                Lippens, Stefaan, Jean-Pierre Martens, and Tom De Mulder. 
                \emph{A comparison of human and automatic musical genre classification.} 
                Acoustics, Speech, and Signal Processing, 2004. Proceedings.(ICASSP'04). IEEE International Conference on. Vol. 4. IEEE, 2004.

        \bibitem{Kour2015}
                Kour, Gursimran, and Neha Mehan. 
                \emph{Music Genre Classification using MFCC, SVM and BPNN.} 
                International Journal of Computer Applications (0975–8887) Volume (2015).

        \bibitem{Logan2000}
                Logan, Beth. 
                \emph{Mel Frequency Cepstral Coefficients for Music Modeling.} 
                ISMIR. 2000.

        \bibitem{Li2003}
                Li, Tao, Mitsunori Ogihara, and Qi Li. 
                \emph{A comparative study on content-based music genre classification.} 
                Proceedings of the 26th annual international ACM SIGIR conference on Research and development in informaion retrieval. ACM, 2003.

        \bibitem{Anglade2010}
                Anglade, Amélie, et al. 
                \emph{Improving music genre classification using automatically induced harmony rules.} 
                Journal of New Music Research 39.4 (2010): 349-361.

        \bibitem{muller2011}
                Muller, Mathias, et al. 
                \emph{Signal processing for music analysis.}, 
                Selected Topics in Signal Processing, IEEE Journal of 5.6 (2011): 1088-1110.

        \bibitem{dooling2014}
                Dooling, Robert J and Stewart H Hulse. 
                \emph{The Comparative Psychology Of Audition.} 
                Hillsdale, N.J.: L. Erlbaum Associates, 1989. Print.

        \bibitem{prasad2007}
                Prasad, Bhanu, and SR Mahadeva Prasanna, eds. 
                \emph{Speech, audio, image and biomedical signal processing using neural networks.} 
                Vol. 83. Springer, 2007.

        \bibitem{Neumayer2004}
                Neumayer, Robert. 
                \emph{Musical genre classification.} 
                (2004).

        \bibitem{Koerich2013}
                Koerich, Alessandro L. 
                \emph{Improving the Reliability of Music Genre Classification using Rejection and Verification.} 
                ISMIR. 2013.

        \bibitem{Haggblade2011}
                Haggblade, Michael, Yang Hong and Kenny Kao. Music genere classification.
                \emph{Department of Computer Science},
                Stanford University,
                2011.

        \bibitem{Nasridinov2014}
                Nasridinov, Aziz, and Young-Ho Park. 
                \emph{A Study on Music Genre Recognition and Classification Techniques.} 
                International Journal of Multimedia and Ubiquitous Engineering 9.4 (2014): 31-42.

        \bibitem{LiTao2003}
                Li, Tao, and George Tzanetakis. 
                \emph{Factors in automatic musical genre classification of audio signals.} 
                Applications of Signal Processing to Audio and Acoustics, 2003 IEEE Workshop on.. IEEE, 2003.

        \bibitem{Downie2003}
                Downie, J. Stephen. 
                \emph{Toward the scientific evaluation of music information retrieval systems.} 
                ISMIR. 2003.

        \bibitem{Tzanetakis1992}
                Tzanetakis, George, and Perry Cook, Musical genre classification 
                \emph{Journal of Personality},
                60(2):225–251,
                1992.

        \bibitem{Ekman1992}
                Ekman, Paul. 
                \emph{Are there basic emotions?.} 
                (1992): 550.

        \bibitem{Russell1980}
                James A. Russell. 
                \emph{A circumplex model of affect.} 
                Journal of Personality and Social Psychology, 39(6): 1161-1178, 1980.

        \bibitem{Thayer1990}
                Thayer, Robert E. 
                \emph{The biopsychology of mood and arousal.} 
                Oxford University Press, 1990.

        \bibitem{Juslin2001}
                Juslin, Patrik N., and John A. Sloboda. 
                \emph{Music and emotion: Theory and research.} 
                Oxford University Press, 2001.

        \bibitem{Lu2006}
                Lu, Lie, Dan Liu, and Hong-Jiang Zhang. 
                \emph{Automatic mood detection and tracking of music audio signals.} 
                IEEE Transactions on audio, speech, and language processing 14.1 (2006): 5-18.

        \bibitem{Fu2011}
                Fu, Zhouyu, et al. 
                \emph{A survey of audio-based music classification and annotation.} 
                IEEE Transactions on Multimedia 13.2 (2011): 303-319.

        \bibitem{Soleymani2013}
                Soleymani, Mohammad, et al. 
                \emph{1000 songs for emotional analysis of music.} 
                Proceedings of the 2nd ACM international workshop on Crowdsourcing for multimedia. ACM, 2013.

        \bibitem{Apon2006}
                Apon, Amy, et al. 
                \emph{Inital Starting Point Analysis for K-Means Clustering: A Case Study.} 
                (2006).

        \bibitem{Jain2010}
                Jain, Anil K. 
                \emph{Data clustering: 50 years beyond K-means.} 
                Pattern recognition letters 31.8 (2010): 651-666.

        \bibitem{Hamerly2002}
                Hamerly, Greg, and Charles Elkan. 
                \emph{Alternatives to the k-means algorithm that find better clusterings.} 
                In Proceedings of the eleventh international conference on Information and knowledge management, pp. 600-607.
                ACM, 2002.

\end{thebibliography}
