\newpage
\section*{ACKNOWLEDGMENT}
\addcontentsline{toc}{section}{\numberline{} ACKNOWLEDGMENT}

It has been a great pleasure to work with different individuals whose perpective and ideas has directly or indirectly assisted or motivated us. 
We would like to gratitude to everyone whose ideas lead to this completion of the project. It is a matter of fact a great privilege for us to 
acknowledge their assistance and contributions to our project.\\
\\
First and foremost, we would like to express our sincere gratitude towards Dr. Basanta Joshi, our supervisor under whose supervision there was successful completion of our project. Without his
invaluable guidance and suggestions, it would have been a difficult journey for us. His useful suggestions for this whole work and cooperative
behavior are sincerely acknowledged.\\
\\
We would like to thank the Department of Electronics and Computer Engineering for adding this major project as part of final year curriculum
and hence giving us this opportunity to undertake the project. The great need of research, time and sheer coding has allowed us to harness our
skills, experience and knowledge.\\ 
\\
We are also grateful to Dr. Nanda Bikram Adhikari for letting us carry out this project and co-operating with us to carry out the project smoothly. We would like to thank and express our gratitude  to all out
respective subject teachers for sharing their precious knowledge, constant support and guidance.\\
\\
Last but not the least, we would like to thank our friends for motivating us and providing numerous assistance throughout the project development duration.\\


